---
output: 
  word_document:
    reference_docx: "..\\doc_styles\\word_styles_FDS_break.docx"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, fig.cap = TRUE, fig.align = 'center')
library(flextable)
library(tidyverse)

tab_weight <- readRDS(".\\tab_weight.rds")
list_lgageparams <- readRDS(".\\lengthage\\list_lgageparams.rds")
```

#########
Table 11.- Regression parameters for log weight (kg) on log length (cm) for primary rockfish species, 1996-2019.
```{r}
tab_weight %>%
  flextable() %>%
    set_header_labels(values = list(spp = "Species", N = "N", 
                           mean_a = "a", sd_a = "sd(a)", 
                           mean_b = "b", sd_b = "sd(b)", 
                           mean_df = "df", sd_df = "sd(df)", 
                           mean_sigma = "\U03C3", sd_sigma = "sd(\U03C3)")) %>%
    align(j = 2:10, align = "right") %>%
    colformat_double(j =2:10, digits = 3) %>%
    line_spacing(space = 0.5) %>%
    font(fontname = "Times New Roman") %>%
    fontsize(size = 10) %>%
    autofit()
```

\newpage

#########
Table xx.- Regression parameters for Von-Bertalanffy length(cm)-at-age relationship for black rockfish by port and sex, 1996-2019.
```{r}
flextable(list_lgageparams[[1]]) %>%
  set_header_labels(values = list(sex = "Sex",
                                  port = "Port", 
                                  Linf_val = "Mean", 
                                  Linf_LCI = "Lower", 
                                  Linf_UCI = "Upper", 
                                  K_val = "Mean", 
                                  K_LCI = "Lower", 
                                  K_UCI = "Upper", 
                                  t0_val = "Mean", 
                                  t0_LCI = "Lower", 
                                  t0_UCI = "Upper")) %>%
  add_header_row(values = c("", "95% CI", "", "95% CI", "", "95% CI"), colwidths = c(3, 2, 1, 2, 1, 2)) %>%
  add_header_row(values = c("", "Linf", "K", "t0"), colwidths = c(2, 3, 3, 3)) %>%
  colformat_double(j = c(3:5, 9:11), digits = 1) %>%
  colformat_double(j = 6:8, digits = 3) %>%
  align(align = "center", part = "header") %>%
  font(fontname = "Times New Roman") %>%
  fontsize(size = 10) %>%
  vline(j = c(2, 5, 8), part = "body") %>%
  vline(i = 1, j = c(2, 5, 8), part = "header") %>%
  vline(i = 2, j = c(2, 3, 5, 6, 8, 9), part = "header") %>%
  vline(i = 3, j = c(2, 5, 8), part = "header") %>%
  merge_v(j = ~ port) %>%
  valign(j = 1, valign = "top", part = "body") %>%
  autofit()
```
 
\newpage
 
Table xx.- Regression parameters for Von-Bertalanffy length(cm)-at-age relationship for black rockfish, 1996-2019.
```{r}
list_lgageparams[[2]] %>%
  flextable() %>%
    set_header_labels(values = list(var = "Parameter", 
                                    val = "Mean", 
                                    LCI = "Lower CI Bound (95%)", 
                                    UCI = "Upper CI Bound (95%)")) %>%
    align(j = 2:4, align = "right") %>%
    colformat_double(j =2:4, digits = 3) %>%
    line_spacing(space = 0.5) %>%
    font(fontname = "Times New Roman") %>%
    fontsize(size = 10) %>%
    autofit()
```

\newpage

#########
Table yy.- Regression parameters for Von-Bertalanffy length(cm)-at-age relationship for yelloweye rockfish by port and sex, 1996-2019.
```{r}
flextable(list_lgageparams[[3]]) %>%
  set_header_labels(values = list(sex = "Sex",
                                  port = "Port", 
                                  Linf_val = "Mean", 
                                  Linf_LCI = "Lower", 
                                  Linf_UCI = "Upper", 
                                  K_val = "Mean", 
                                  K_LCI = "Lower", 
                                  K_UCI = "Upper", 
                                  t0_val = "Mean", 
                                  t0_LCI = "Lower", 
                                  t0_UCI = "Upper")) %>%
  add_header_row(values = c("", "95% CI", "", "95% CI", "", "95% CI"), colwidths = c(3, 2, 1, 2, 1, 2)) %>%
  add_header_row(values = c("", "Linf", "K", "t0"), colwidths = c(2, 3, 3, 3)) %>%
  colformat_double(j = c(3:5, 9:11), digits = 1) %>%
  colformat_double(j = 6:8, digits = 3) %>%
  align(align = "center", part = "header") %>%
  font(fontname = "Times New Roman") %>%
  fontsize(size = 10) %>%
  vline(j = c(2, 5, 8), part = "body") %>%
  vline(i = 1, j = c(2, 5, 8), part = "header") %>%
  vline(i = 2, j = c(2, 3, 5, 6, 8, 9), part = "header") %>%
  vline(i = 3, j = c(2, 5, 8), part = "header") %>%
  merge_v(j = ~ port) %>%
  valign(j = 1, valign = "top", part = "body") %>%
  autofit()
```
 
\newpage
 
Table y.- Regression parameters for Von-Bertalanffy length(cm)-at-age relationship for yelloweye rockfish, 1996-2019.
```{r}
list_lgageparams[[4]] %>%
  flextable() %>%
    set_header_labels(values = list(var = "Parameter", 
                                    val = "Mean", 
                                    LCI = "Lower CI Bound (95%)", 
                                    UCI = "Upper CI Bound (95%)")) %>%
    align(j = 2:4, align = "right") %>%
    colformat_double(j =2:4, digits = 3) %>%
    line_spacing(space = 0.5) %>%
    font(fontname = "Times New Roman") %>%
    fontsize(size = 10) %>%
    autofit()
```